%-------------------------------------
% Resum in LaTeX (XeLaTeX)
% Author:  HF Yuan
% Project: https://github.com/xyz-yuanhf/yuan-resume
% Base on: https://github.com/mattyHerzig/mattys_resume
%          http://www.jianxu.net/en/
% License: MIT
%------------------------------------

\documentclass[a4paper, 10pt]{article}
\pagenumbering{gobble}
\usepackage{myresume}  % Style package
\usepackage{csquotes}

% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{flushright}
  \setstretch{0.6}
  \item {\Calluna Drayton House, London}  % E-mail address
  \item {\Calluna zctpanl@ucl.ac.uk}    % Home page
\end{flushright}\vspace{-45pt}

\begin{flushleft}  % Rplace here with your name (and identity if required)
  {\Calluna \fontsize{30pt}{30pt}\selectfont \textsc{Ze Wang}} \quad {\Calluna \fontsize{14.5pt}{14.5pt}\selectfont}
  \noindent\rule{\textwidth}{0.4pt}
\end{flushleft}

% -------------------- EDUCATION --------------------
\sectionBlock{
\section{Education}
}{
\pubListStart
\justifying
\item[]   Ph.D. in Economics, University College London, 2023 - Present 
\item[]   MSc in Economics (Distinction), University College London, 2023
\item[]   BSc  in Economics (First Class), University College London, 2022
\pubListEnd
}

\sectionBlock{
\section{Employment}
}{
\pubListStart
\justifying
\item[] Research Fellow, Institute for the Future of Work, 2025-
\item[] Research Affiliate, Holistic AI, 2024- 
\pubListEnd
}

% -------------------- PUBLICATIONS --------------------
\sectionBlock{
\section{Publications}
}{
\pubListStart
\justifying
\item[] 
\item[] Ze Wang, Zekun Wu, Yichi Zhang, Xin Guan, Navya Jain, Qinyang Lu, Saloni Gupta, Adriano Koshiyama. ``Bias Amplification: Large Language Models as Increasingly Biased Media.''
 \textit{Proceedings of the 14th International Joint Conference on Natural Language Processing and the 4th Conference of the Asia-Pacific Chapter of the Association for Computational Linguistics.}
\item[] Ze Wang, Zekun Wu, Xin Guan, Michael Thaler, Adriano Koshiyama, Skylar Lu, Sachin Beepath, Ediz Ertekin, and Maria Perez-Ortiz. ``JobFair: A Framework for Benchmarking Gender Hiring Bias in Large Language Models.'' \textit{Findings of the association for computational linguistics: EMNLP 2024.}
\pubListEnd
}

\sectionBlock{
\section{Works in progress}
}{
\pubListStart
\justifying
\item[] Ze Wang, Guobin Shen, and Michael Thaler. ``Large Language Models in Hiring.''
\item[] Ze Wang. ``Human-AI Interaction Experiments.''
\item[] Michael Thaler and Ze Wang. ``AI and Politics.''
\item[] Marcos Vera Hernandez, Soledad Giardili, and Ze Wang. ``AI and Education.''
\item[] Ze Wang and Zekun Wu. ``An Evaluation Benchmark for AI Agents.''

\pubListEnd
}

\sectionBlock{
\section{Grants and Awards}
}{
\pubListStart
\justifying
\item[] Stone PhD Scholarship (Stone Centre at UCL). Overview: This scholarship includes a research grant focused on studying how AI technologies may perpetuate or amplify existing inequalities related to demographic characteristics .
\pubListEnd
}

\sectionBlock{
\section{Teaching}
}{
\pubListStart
\justifying
\item[] \textbf{UCL:} Teaching Assistant, \textit{Statistical Methods in Economics} (ECON0005) 
\pubListEnd
}

\sectionBlock{
\section{Presentations}
}{
\pubListStart
\justifying
\item[] \textbf{2025:} Stone Centre at UCL; University College London 
\item[] \textbf{2024:}  Holistic AI; University College London 
\pubListEnd
}

\end{document}

